Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-27 inst/paper/main.tex
move

\textit{Environments.} In R, environments can be accessed, manipulated and created at will. Each function has a corresponding environment, which inherits from its calling function. In the scope of the function, it can be accessed with \c{environment()}.  A new environment, which by default inherits from the current environment, is created with \c{new.env}. Contrary to other values, environments in R follow a \emph{reference semantics}, not a \emph{copy semantics}. The chain of inheriting environments can be climbed up with \c{parent.env}, and ultimately, one arrives at \c{emptyenv}, the empty environment. Functions such as \c{parent.frame} and \c{sys.frame} also make it possible to access environments further up in the calling stack, up to the global environment \c{.GlobalEnv}, enabling \emph{dynamic scoping}.
One can also directly read, modify or create new bindings in any environments. Given an environment \c{e}:

\begin{itemize}
	\item  \c{e$v} or \c{get("v", envir = e)} reads variable \c{v} in \c{e};
	\item \c{e$v <- 2} or \c{assign("v", 2, envir = e)} writes value 2 in variable \c{v} in \c{e}. \c{v} is created if it did not exist in \c{e}. %if argument inherits = TRUE, then if v exists in a parent environment, that binding is modified, instead of creating a new one
\end{itemize}

@@

The second substantial difference is the control that R gives over the
choice of environment in which the AST is evaluated in. Beside
traditional choices such as the top level or current lexical
environment, R allows programmers to choose a fresh, empty,
environment or any environment on the call stack. This is a
significant increase in expressive power as functions that are
otherwise not aware of the use of \eval may be deeply impacted.

>>>>

@@

\medskip\noindent\textit{Environments.} In R, environments can be
accessed, manipulated and created at will. Each function has a
corresponding environment, which inherits from its calling function.
In the scope of the function, it can be accessed with
\c{environment()}. A new environment, which by default inherits from
the current environment, is created with \c{new.env}. Contrary to
other values, environments in R follow a \emph{reference semantics},
not a \emph{copy semantics}. The chain of inheriting environments can
be climbed up with \c{parent.env}, and ultimately, one arrives at
\c{emptyenv}, the empty environment. Functions such as
\c{parent.frame} and \c{sys.frame} also make it possible to access
environments further up in the calling stack, up to the global
environment \c{.GlobalEnv}, enabling \emph{dynamic scoping}. One can
also directly read, modify or create new bindings in any environments.
Given an environment \c{e}:

\begin{itemize}
	\item  \c{e$v} or \c{get("v", envir = e)} reads variable \c{v} in \c{e};
	\item \c{e$v <- 2} or \c{assign("v", 2, envir = e)} writes value 2 in variable \c{v} in \c{e}. \c{v} is created if it did not exist in \c{e}.
\end{itemize}
